---
title: "Eyetracker Data Preprocessing"
author: "Ari Dyckovsky"
output:
  md_document:
    variant: markdown_github
---

# Eyetracker Data Preprocessing

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  strip.white = TRUE,
  tidy = TRUE,
  highlight = TRUE
)
```

## Load packages

```{r, libraries, message=FALSE}
library(tidyverse)
library(formatR)
```

## File path definitions

```{r}
root_path <- "/Volumes/shlab/Projects/CSN/data/extracted/eyetracker"
event_csv <- "fevent.csv"
sample_csv <- "fsample.csv"
ioevent_csv <- "ioevent.csv"
recordings_csv <- "recordings.csv"

id_prefix <- "CSN"
id_length <- 3
min_id <- 1
max_id <- 57
```

## Loading methods

```{r}
get_path_to_id <- function(id) {
  padded_id <- stringr::str_pad(id, 3, pad = "0")
  participant_id <- stringr::str_c(id_prefix, padded_id)
  return(file.path(root_path, participant_id))
}

get_id_vector <- function() {
  # Gets a vector of id integers for participants
  id_vector <- c()
  for (i in min_id:max_id) {
    if ( dir.exists(get_path_to_id(i)) ) {
      id_vector <- c(id_vector, i)
    }
  }
  return(id_vector)
}

load_all_etd_by_filename_csv <-function(id_vector, filename_csv = sample_csv) {
  # Loads all eyetracking data of given filename across participants
  etd_list <- list()
  for (id in id_vector) {
    path_to_etd <- file.path(get_path_to_id(id), filename_csv)
    etd_list[[id]] <- readr::read_csv(path_to_etd)
  }
  return(etd_list)
}

# Convenience instantiation of the id vector for later use. Can use
# the getter method at any point for same output.
id_vector <- get_id_vector()
```

## Load each data for all participants

```{r, message=FALSE}
etd_events <- load_all_etd_by_filename_csv(id_vector, event_csv)
etd_ioevents <- load_all_etd_by_filename_csv(id_vector, ioevent_csv)
etd_recordings <- load_all_etd_by_filename_csv(id_vector, recordings_csv)
# TAKES A LOT OF TIME TO LOAD. UNCOMMENT IF WANTED.
#etd_samples <- load_all_etd_by_filename_csv(id_vector, sample_csv)
```

### Events data methods using `edt_events` list

```{r, events-data-methods}
CALIBRATION_RESULT_MESSAGE <- "!CAL CALIBRATION HV9 R RIGHT"
VALIDATION_RESULT_MESSAGE <- "!CAL VALIDATION HV9 R RIGHT"
CATEGORY_STRING_PATTERN <- "CALIBRATION|VALIDATION"
QUALITY_STRING_PATTERN <- "GOOD|FAIR|POOR"
AVG_ERROR_STRING_INDEX <- 8
MAX_ERROR_STRING_INDEX <- 10
DEG_OFFSET_STRING_INDEX <- 13
PIX_OFFSET_STRING_INDEX <- 15


get_category_from_message <- function(message) {
  # Extract the category of event message
  as.character(str_extract(message, CATEGORY_STRING_PATTERN))
}


get_quality_from_message <- function(message) {
  # Extract the quality of calibration or validation from event message
  as.character(str_extract(message, QUALITY_STRING_PATTERN))
}


get_avg_error_from_message <- function(message) {
  # Extract the avg error of validation
  as.double(word(message, AVG_ERROR_STRING_INDEX))
}


get_max_error_from_message <- function(message) {
  # Extract the max error of validation
  as.double(word(message, MAX_ERROR_STRING_INDEX))
}


get_deg_offset_from_message <- function(message) {
  # Extract the deg offset of validation
  as.double(word(message, DEG_OFFSET_STRING_INDEX))
}


get_pix_offset_from_message <- function(message) {
  # Extract the x coordinate of pix offset of validation
  word(message, PIX_OFFSET_STRING_INDEX)
}


get_event_messages <- function(participant_events) {
  # Get the significant event messages for a single participant
  # events data by sttime, producing extracted columns from
  # message contents.
  participant_events %>%
    select(message, sttime) %>%
    transmute(message = str_squish(str_trim(message)), sttime = sttime) %>%
    filter(str_detect(message, CALIBRATION_RESULT_MESSAGE) | str_detect(message, VALIDATION_RESULT_MESSAGE)) %>%
    mutate(
      category = get_category_from_message(message),
      quality = get_quality_from_message(message),
      avg_error = get_avg_error_from_message(message),
      max_error = get_max_error_from_message(message),
      deg_offset = get_deg_offset_from_message(message),
      pix_offset = get_pix_offset_from_message(message)
    ) %>%
    separate(pix_offset, c("pix_x_offset", "pix_y_offset"), ",") %>%
    mutate(
      pix_x_offset = as.double(pix_x_offset),
      pix_y_offset = as.double(pix_y_offset)
    ) %>%
    relocate(-message)
}
```

```{r}
# Output a single participant's important calibration/validation info
get_event_messages(etd_events[[1]]) 
```

### Recordings data methods using `etd_recordings` list

```{r, recordings-data-methods}
get_duration <- function(id) {
  # Duration from highest start time and lowest start time, in minutes
  summary <- etd_recordings[[id]] %>% 
    summarize(duration = (max(time) - min(time)) / (1000*60) ) %>%
    unnest(cols = c())
  return(summary$duration)
}

get_durations <- function(id_vector) {
  # Durations in minutes for all participants events' data
  durations <- c()
  for (i in id_vector) {
    durations <- c(durations, get_duration(i))
  }
  return(durations)
}

get_recording_time_matrix <- function(id_vector, dimensional_reducer = 1) {
  # Get a built matrix with a row for each id in id_vector, with four
  # times per row. Optional dimensional reducer to achieve times in seconds, minutes.
  n_ids <- length(id_vector)
  n_recordings <- 1 + length(etd_recordings[[id_vector[[1]]]]$time)
  recording_time_matrix <- matrix(NA, nrow=n_ids, ncol=n_recordings)
  
  for (i in 1:n_ids) {
    id <- id_vector[i]
    recording_time_matrix[i,] <- c(id, (etd_recordings[[id]]$time / dimensional_reducer))
  }
  
  return(recording_time_matrix)
  
}

get_recording_time_df <- function(id_vector, dimensional_reducer = 1) {
  # Get dataframe using matrix of ids and times from recordings. Optional
  # dimensional reducer to achieve times in seconds, minutes.
  m <- get_recording_time_matrix(id_vector, dimensional_reducer)
  df <- as.data.frame(m)
  recording_time_df_cols <- c("id", "calibration", "validation", "task", "revalidation")
  colnames(df) <- recording_time_df_cols
  
  return(df)
  
}
```

### Look at recording times

Can retrieve all recording moments across participants by seconds or minutes. In seconds, the difference between revalidation and task time, then subtracting 3600, provides an idea of how much "overtime" the task went.

```{r}
recording_time_df_seconds <- get_recording_time_df(id_vector, 1000)
recording_time_df_minutes <- get_recording_time_df(id_vector, 1000 * 60)

sort(recording_time_df_seconds$revalidation - recording_time_df_seconds$task - 3600)
```

## Joint data methods

```{r, joint-data-methods}
get_times_with_validations_for_id <- function(recording_time_df, i) {
  
  recording_times_for_id <- recording_time_df %>%
    filter(id == i)
  
  validated_participant_details <- get_event_messages(etd_events[[i]]) %>%
    filter(category == "VALIDATION") %>%
    arrange(sttime) %>%
    slice_tail(n = 2) %>%
    mutate(id = as.integer(i)) %>%
    relocate(id)
  
  times_with_validations <- validated_participant_details %>%
    inner_join(recording_times_for_id) %>%
    select(-c(message, category)) %>% # dropped cols from events
    select(-c(calibration, validation)) %>%# dropped cols from recordings
    rename_at(vars(task, revalidation), ~ paste0(., "_start_time")) %>%
    mutate(id = as.integer(id)) %>%
    relocate(id, sttime, task_start_time, revalidation_start_time)
  
  return(times_with_validations)
  
}


get_all_times_with_validations <- function(id_vector) {
  df <- data.frame()
  recording_time_df <- get_recording_time_df(id_vector)
  for (i in id_vector) {
    times_with_validations <- get_times_with_validations_for_id(recording_time_df, i)
    df <- bind_rows(df, times_with_validations)
  }
  return(df)
}
```

### Combine recording times with significant event details per participant

```{r, combine-recording-events, message=FALSE}
# For demonstartion purposes, first 10 rows
get_all_times_with_validations(id_vector) %>% slice_head(n = 10)
```


