---
title: "Behavioral Data Analysis"
author: "Ari Dyckovsky"
---

```{r, setup, include=FALSE}
# Knitr options
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  #echo = FALSE,
  strip.white = TRUE,
  highlight = TRUE
)

options(knitr.table.format = "markdown")

# Load packages
library(targets)
library(here)
library(withr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(summarytools)
library(lme4)
library(lmerTest) # adds useful info to lme4 output
library(sjPlot)
library(ggeffects)

# R options
options(
  width = 90
)

# summarytools options
st_options(
  plain.ascii = FALSE
)

# ggplot options
ggplot2::theme_set(theme_minimal())
```

## Read extracted behavioral data

Use `tar_read` to get the target object `combined_behavioral_data` and assign it to `combined_df`.

```{r load-data}
withr::with_dir(here::here(), {
  combined_df <- tar_read(combined_behavioral_data)
})
```

## Models

We read in and summarize models already evaluated from the `analyze_behavioral_data` target list in `_targets.R`.

### Predict the probability of a hit by signal time

```{r}
withr::with_dir(here::here(), {
  broom.mixed::tidy(tar_read(model_hit_by_signal_time))
})
```

```{r}
withr::with_dir(here::here(), {
  ggpredict(tar_read(model_hit_by_signal_time), 'signal_time') %>%
    plot()
})
```

### Predict the probability of a hit by signal time (with random effects on signal time)

```{r}
withr::with_dir(here::here(), {
  broom.mixed::tidy(tar_read(model_hit_by_signal_time_rfx))
})
```

```{r}
withr::with_dir(here::here(), {
  ggpredict(tar_read(model_hit_by_signal_time_rfx), 'signal_time') %>%
    plot()
})
```

### Predict reaction time using signal time

```{r}
withr::with_dir(here::here(), {
  broom.mixed::tidy(tar_read(model_reaction_time_by_signal_time))
})
```

```{r}
withr::with_dir(here::here(), {
  ggpredict(tar_read(model_reaction_time_by_signal_time), 'signal_time') %>%
    plot()
})
```

### Predict reaction time using signal time (with random effects on signal time)

```{r}
withr::with_dir(here::here(), {
  broom.mixed::tidy(tar_read(model_reaction_time_by_signal_time_rfx))
})
```

```{r}
withr::with_dir(here::here(), {
  ggpredict(tar_read(model_reaction_time_by_signal_time_rfx), 'signal_time') %>%
    plot()
})
```

### Predict the probability of a false alarm by response time

```{r}
withr::with_dir(here::here(), {
  broom.mixed::tidy(tar_read(model_false_alarm_by_response_time))
})
```

```{r}
withr::with_dir(here::here(), {
  ggpredict(tar_read(model_false_alarm_by_response_time), 'resp_time') %>%
    plot()
})
```

### Predict the probability of a false alarm by response time (with random effects on response time)

```{r}
withr::with_dir(here::here(), {
  broom.mixed::tidy(tar_read(model_false_alarm_by_response_time_rfx))
})
```

```{r}
withr::with_dir(here::here(), {
  ggpredict(tar_read(model_false_alarm_by_response_time_rfx), 'resp_time') %>%
    plot()
})
```
