---
title: "Behavioral Data Analysis"
author: "Ari Dyckovsky"
---

```{r, setup, include=FALSE}
# Knitr options
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  #echo = FALSE,
  strip.white = TRUE,
  highlight = TRUE
)

options(knitr.table.format = "markdown")

# Load packages
library(targets)
library(here)
library(withr)
library(tidyverse)
library(broom)
library(summarytools)
library(lme4)
library(lmerTest) # adds useful info to lme4 output

# R options
options(
  width = 90
)

# summarytools options
st_options(
  plain.ascii = FALSE
)
```

## Read extracted behavioral data

Use `tar_read` to get the target object `extracted_behavioral_data_combined` and assign it to `combined_df`.

```{r load-data}
withr::with_dir(here::here(), {
  combined_df <- tar_read(extracted_behavioral_data_combined)
})
```

### Sanity checks for extracted data

Look at a few rows of data to verify output format.

```{r see-data}
knitr::kable(head(combined_df))
```

Check count of participants by unique id.

```{r, count-participants}
length(unique(combined_df$id))
```

## Analyze all participants' hits with reaction times

Read targets object `all_hits_with_reaction_times` and assign to the combined hits dataframe `combined_hits_df`.

```{r read-combined-hits}
withr::with_dir(here::here(), {
  combined_hits_df <- tar_read(all_hits_with_reaction_times)
})
```

Check out a quick preview of the table of hits

```{r preview-combined-hits}
knitr::kable(head(combined_hits_df))
```

Check out the reaction time summary statistics by id:

```{r summary-stats-combined-hits}
combined_hits_df %>%
    drop_na() %>%
    group_by(id) %>%
    summarise(
      reaction_time_mean = mean(reaction_time),
      reaction_time_min = min(reaction_time),
      reaction_time_max = max(reaction_time),
      reaction_time_sd = sd(reaction_time)
    ) %>%
  head() %>%
  knitr::kable()
```

Check plot of all reaction times by signal times. (Note the 100ms gaps where responses were not recorded at 1-1.1, 2-2.1, ...)

```{r all-reaction-times-by-signal-times-plot}
combined_hits_df %>%
  drop_na() %>%
  ggplot(aes(x = signal_time, y = reaction_time)) +
    geom_point(color = 'orange') +
    geom_smooth(method=lm) +
    theme_classic()
```

## Reaction times per participant centered at the median

```{r boxplot-reaction-times, fig.height = 10, fig.width = 10}
combined_hits_df %>%
  drop_na() %>%
  arrange(reaction_time) %>%
  ggplot(aes(x = reorder(id, reaction_time, FUN = median), y = reaction_time)) +
    geom_point(alpha = 0.8, size = 0.7, color = 'darkblue', position = 'jitter') +
    geom_boxplot(alpha = 0) +
    geom_hline(yintercept = 1, color = 'coral') +
  theme_minimal() +
  theme(
    aspect.ratio = 1,
    text = element_text(size = 15),
    plot.margin = margin(18, 18, 18, 18, 'pt')
  ) +
  labs(
    title = 'Reaction times of participants by id',
    subtitle = 'Boxplot per participant anchored at median of reaction time',
    y = 'Reaction time for HIT after double-tick signal',
    x = 'Participant'
  ) +
  coord_flip()
```

## Read false alarms target

```{r read-false-alarms}
withr::with_dir(here::here(), {
  false_alarms_df <- tar_read(false_alarms)
})
```

```{r preview-false-alarms}
false_alarms_df %>%
  head() %>%
  knitr::kable()
```

## Models

### Scale times to `[0,1]` interval for modeling

```{r}
# TODO: migrate to functions in `R/`
scaled_combined_hits_df <- combined_hits_df %>%
  mutate(
    signal_time = signal_time / 3600
  )

scaled_false_alarms_df <- false_alarms_df %>%
  mutate(
    resp_time = resp_time / 3600
  )
```

### Predict the probability of a hit by signal time

```{r}
model_pHit_signal_time <- hit_by_signal_time_model(scaled_combined_hits_df)

summary(model_pHit_signal_time)
```

### Predict the probability of a hit by signal time with random effects

```{r}
model_pHit_signal_time_rfx <- hit_by_signal_time_model(
  scaled_combined_hits_df, 
  random_effects = TRUE
)

summary(model_pHit_signal_time_rfx)
```

### Predict reaction time using signal time

```{r}
model_RT_signal_time = reaction_time_by_signal_time_model(
  scaled_combined_hits_df
)

summary(model_RT_signal_time)
```

### Predict reaction time using signal time with random effects

```{r}
model_RT_signal_time_rfx = reaction_time_by_signal_time_model(
  scaled_combined_hits_df,
  random_effects = TRUE
)

summary(model_RT_signal_time_rfx)
```

### Predict the probability of a false alarm by response time

```{r}
model_FA_resp_time = false_alarm_by_response_time_model(
  scaled_false_alarms_df,
  random_effects = FALSE
)

summary(model_FA_resp_time)
```

### Predict the probability of a false alarm by response time with response time random effects

```{r}
model_FA_resp_time_rfx = false_alarm_by_response_time_model(
  scaled_false_alarms_df,
  random_effects = TRUE
)

summary(model_FA_resp_time_rfx)
```

